Investigating Interventions

### 2023-03-01 minos/validation/interventions.Rmd
Moved the code for visualising pathway variable comparisons between baseline and intervention into functions, and moved these functions into validation/utils.r. Then added pathway plots to the other interventions in interventions.Rmd

@@

@@

>>>>

## Pathways

### Housing Quality

```{r}
compare_housing_out(base, energy)
```

### Neighbourhood Safety

```{r}
compare_neighbourhood_out(base, energy)
```

### Tobacco Use

```{r}
compare_ncigs_out(base, energy)
```

### Nutrition Quality

```{r}
compare_nutrition_out(base, energy)
```

### Loneliness (NOT CURRENTLY IN SF12 MODEL)

```{r}
compare_loneliness_out(base, energy)
```

@@

## Pathways

```{r}
compare_housing_out(base, wage)
compare_neighbourhood_out(base, wage)
compare_ncigs_out(base, wage)
compare_nutrition_out(base, wage)
compare_loneliness_out(base, wage)
```

@@

## Pathways

```{r}
compare_housing_out(base, allchild)
compare_neighbourhood_out(base, allchild)
compare_ncigs_out(base, allchild)
compare_nutrition_out(base, allchild)
compare_loneliness_out(base, allchild)
```
